---
title: "12/29
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

#Using the diamonds data set:

Print a data frame that contains the simple count of diamonds in each “cut” (“Fair”, “Good”, etc.).

```{r}
simp_data <- diamonds %>% 
  count(cut)
simp_data
```

The diamonds data set is reasonably big, which is a bit of a pain. Use dplyr functions to create a that contains 1% of the rows of diamonds, randomly subsetted.
# one_percent <- diamonds %>% 

  sample(c("Fair","Ideal","Premium","Good","Very Good"),
         size = n,
         replace = FALSE,
         prob = c(.99,.1))
one_percent

```{r}
one_percent <- diamonds %>% 
  slice_sample(prop = 0.01)
  
  

```

Calculate the average size of the 100 largest diamonds in each clarity category.

```{r}
ave_size_ten_largest <- select(diamonds, clarity, desc(carat), n = 10)
ave_size_ten_largest

```


```{r}
real_ave <- select(diamonds,clarity,carat) %>% 
  filter(desc(carat))
  real_ave
                   
                   
```

```{r}
plot <- ggplot(diamonds, aes(x = clarity, y = carat))+
  geom_point()+
  theme_classic()
plot
```

