---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


# Initializing

Adding the diamonds data set and naming it so we can use it later.
put data set first then pipe that to group function
pipe that to countfunction. Can use summarize function but the exercise is only asking us to count. 

```{r}
diamond_project <- diamonds %>% 
  group_by(cut) %>% 
  count()
diamond_project
``` 

## random sample of the row

using slice function to do this
you can group by and pipe that to slice to manipulate specific properties of my dataset


```{r}
diamond_subset <- diamonds %>% 
  slice_sample(prop=0.01)
```

## Calculate average size

summary within a catagory need group by
100 largest in each category subset dataframe to have 100 rows per catagory slice will help here too
instead of mean can use sd function to get the standard deviation
mean takes a list of numbers and returns a single value anything that makes things a single value can be used in summary function (min, max,etc)
order by argument that slice max takes to pick which column to pick the max from

```{r}
diamond_question_3 <- diamonds %>% 
  group_by(clarity) %>% 
  slice_max(order_by=carat, n=100, with_ties = FALSE) %>% 
  summarise(mean_size=mean(carat))
diamond_question_3
```


## part four to make some scatter plots

do not quote aes argument if it goes in aes i tell ggplot it is coming from the dataset
quotes means it is not coming from the dataset and is coming from something else and the argument should not be in the aes function
if it is in the dataset it also goes in the aes argument for example adding color to the carat output


```{r}
diamond_plots_1 <- ggplot(data=diamonds,mapping=aes(x=x, y=y))+
  geom_point()
diamond_plots_1
diamond_plot_2 <- ggplot(data=diamonds,mapping=aes(x=x, y=z))+
  geom_point()
diamond_plot_2
```

## removing questionable data


filter three times for each of the variables x,y,z
in each filter section can identify the bounds that I want to filter by
piping removes the need to id the dataset in the beginning of the filter function
filter is filtering things that I want I am not specifying what I don't want I am telling it what I do want

```{r}
diamond_filter_1 <- diamonds %>% 
  filter(x>=3) %>% 
  filter(y>1 & y<20) %>% 
  filter(z>1 & z<10)
diamond_filter_1
```

