---
title: "Some math AKA Homework 4"
output: github_document
---
# Homework 4
Homework 4 writing script to do some simple math equations and learning to use functions and make these functions a plot.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(nycflights13)
```

## Calculating the sum
assigning a value to an object and adding two objects together


```{r}
a <- 3
b <- 2
print(a+b)
```

### Sum function


```{r}
sum(2,3)
```


### **Flights**
The code for the library addition might still be in my script I have issues correlating what I write in code with the result. This extra step lets me see the code and see the result together. This next step will add a plot to the code written thus far.

```{r}
AA_flights <- filter(flights, carrier == "AA")
```

**flights is a data set inside the data frame nyc flight.**

```{r}
test_name_plot <- ggplot(data= AA_flights, mapping = aes(x=dep_delay, y=arr_delay))+
  geom_point()
test_name_plot+
  labs(title = "Cool Plot", y= "arrival delays", x= "departure delays")+
  theme_classic()+
  theme(axis.title=element_text(size=24),
        axis.text=element_text(size=20,color="purple"), 
        plot.title = element_text(size = 28, hjust = .5) )


```




