---
title: "Homework_8"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(broom)
library(nls2)
library(patchwork)
```

# Start with what you know.

This was a little confusing until you did it with the penguins.  I think the DNase and biology stuff was confusing.

You can compare things like how you did the bill length and species in the penguin exercises. 

models_penguins <- penguins %>% 
  group_by(species) %>% 
  nest() %>% 
  mutate(models = map(data, ~lm(bill_length_mm ~ body_mass_g, data = .x)),
         coefficients = map(models, ~tidy(.x)),
         slope = map_dbl(coefficients, ~pull(.x, estimate)[2])) %>% 
  arrange(desc(slope))
  
## Notes
 Group_by and Filter_by are confusing.
 Filter when you want to exclude something.
 
group_by I have a structure in my data set and I want r to know about it because i am going to do something to each group in the data.

The thing I am going to do to my data I want to do to the group NOT the whole data set.

```{r}

diamonds_start <- diamonds %>% 
  group_by(color) %>% 
  nest() %>% 
  mutate(models = map(data, ~lm( price~ carat, data = .x)),
         coefficients = map(models, ~tidy(.x)),
         slope = map_dbl(coefficients, ~pull(.x, estimate)[2])) %>% 
  arrange(desc(slope))
diamonds_start
```

## The above code generates a table
A table to which I have added (mutated) the column slope in descending order.

# Non linear 

```{r}
library(nls2)
library(broom)
library(tidyverse)

monod_mod <- formula(density ~ (conc*dmax)/(conc + k))

sqrt_mod <- formula(density ~ beta_1 * sqrt(conc) + beta_0)
single_sqrt_model <- nls2(sqrt_mod,
data = DNase,
start = list(beta_1 = 0.5, beta_0 = 0.1)) 

compare_models <- DNase %>%
  group_by(Run) %>%
  nest() %>%
  mutate(sqrt_mod = map(data, ~ nls2(
    sqrt_mod,
    data = .,
    start = list(beta_1 = 0.5, beta_0 = 0.1)
  )),
  monod_mod = map(data,  ~ nls2(
    monod_mod, data = ., start = list(dmax = .3, k = .4)
  )), 
  sqrt_aic= map_dbl(sqrt_mod,~glance(.)$AIC), 
  monod_aic=map_dbl(monod_mod,~glance(.)$AIC))
compare_models
```

# Build the Plots for comparison

```{r}
plot_monod_model <- ggplot(compare_models,aes(x=Run, y=monod_aic))+
  geom_point()+
  theme_classic()+
  labs(title="Monod AIC Per Run", y= "Monod AIC", x="Run Number")+
  theme(plot.title = element_text(size = 10, hjust = .5))
plot_monod_model

  plot_squareroot_model <- ggplot(compare_models,aes(x=Run, y=sqrt_aic))+
  geom_point()+
  theme_classic()+
  labs(title="Squareroot AIC Per Run", y= "Squareroot AIC", x="Run Number")+
  theme(plot.title = element_text(size = 10, hjust = .5))
plot_squareroot_model

plot_monod_model+plot_squareroot_model

```

Monod Model appears to have the most negative values and is the best model to use. Runs 4 and 5 were particularly good and we should attempt to replicate them.

