---
title: "Olivine_avecomp_tern_ca-in-ol-temp"
output: github_document
---
2-10-22

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggtern)
```
### CPX and OL together on a table is not tidy. Is it ok practice to put OL always first on a table and then filter out the rows I want and differentiate between rows of cpx and ol?


#Olivine
## Average composition

```{r}
mol_numbers <- mutate(M5_DE_all_CPX_KBH_94_23, P2O5/141.943,#Change file here
                  SiO2/53.083,
                  TiO2/79.865,
                  Al2O3/101.961,
                  Cr2O3/99.993,
                  MgO/40.304,
                  CaO/56.077,
                  MnO/70.937,
                  FeO/71.844,
                  NiO/74.692,
                  Na2O/61.979,
                  K2O/94.195)

oxygen_number <- mutate(mol_numbers, p = P2O5/141.943*5,
                        si = SiO2/53.083 * 2,
                        ti = TiO2/79.865 * 2,
                        al = Al2O3/101.961 * 3,
                        cr = Cr2O3/99.993 * 3,
                        mg = MgO/40.304 * 1,
                        ca = CaO/56.077 * 1,
                        mn = MnO/70.937 * 1,
                        fe = FeO/71.844 * 1,
                        ni = NiO/74.692 * 1,
                        na = Na2O/61.979 * 1,
                        k = K2O/94.195 * 1
                        )

sum_ox <- select(oxygen_number, p,
                   si,
                   ti,
                   al,
                   cr,
                   mg,
                   ca,
                   mn,
                   fe,
                   ni,
                   na,
                   k
                   )

sum_row <- sum_ox %>% 
  mutate(sum = rowSums(.))

#CHANGE BASED ON PYX=6 OL/SPI=4

six_div_sum <- mutate(sum_row,norm_constant = 4/sum) %>% 
  select(norm_constant)

six_div_sum_oxygen_number <- bind_cols(oxygen_number,six_div_sum)

oxy_num_mult_norm_const <- mutate(six_div_sum_oxygen_number, a = p*norm_constant,
                                  b = si*norm_constant,
                                  c = ti*norm_constant,
                                  d = al*norm_constant,
                                  e = cr*norm_constant,
                                  f = mg*norm_constant,
                                  g = ca*norm_constant,
                                  h = mn*norm_constant,
                                  i = fe*norm_constant,
                                  j = ni*norm_constant,
                                  k = na*norm_constant,
                                  l = k*norm_constant
                                  )

mult_cations <- mutate(oxy_num_mult_norm_const, a1 = a * 2/5,
                       a2 = b * 1/2,
                       a3 = c * 1/2,
                       a4 = d * 2/3,
                       a5 = e * 2/3,
                       a6 = f * 1/1,
                       a7 = g * 1/1,
                       a8 = h * 1/1,
                       a9 = i * 1/1,
                       a10 = j * 1/1,
                       a11 = k * 2/1,
                       a12 = l * 2/1)

end <- mult_cations %>% 
  summarise(ave_P = mean(a1),
            ave_Si = mean(a2),
            ave_Ti = mean(a3),
            ave_Al = mean(a4),
            ave_Cr = mean(a5),
            ave_Mg = mean(a6),
            ave_Ca = mean(a7),
            ave_Mn = mean(a8),
            ave_Fe = mean(a9),
            ave_Ni = mean(a10),
            ave_Na = mean(a11),
            ave_K = mean(a12) 
            )

show_tbl_1 <- knitr::kable(end)
show_tbl_1
```

# Ol ternary

```{r}
MgO_num <- mutate(M5_DE_all_pyx_KBH_94_23, mg_dat = MgO/40.304,
                  fe_dat = FeO/71.844,
                  ca_dat = CaO/56.077,
                  Mg = (mg_dat/(mg_dat+fe_dat+ca_dat))*100,
                  Fe = (fe_dat/(mg_dat+fe_dat+ca_dat))*100,
                  Ca = (ca_dat/(mg_dat+fe_dat+ca_dat))*100
                  )
                  
#MgO_num %>% 
 # kbl() %>% 
  #kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
show_tbl_1 <- knitr::kable(MgO_num)#%>%
   #kable_material(c("striped", "hover"))
  #kable_styling()
  #kable_styling(font_size = 7)
  #kable_styling(latex_options="scale_down")
show_tbl_1

  tern <- ggtern(data = MgO_num, aes(x = Mg,
                          y = Ca, 
                          z = Fe)) +
  geom_point()+
    labs(title = "CPX and OPX")+
    theme_bw()
  
  tern
```


# Ca in Olivine thermometer
## start with atomic proportion of ca in ol. Bring in another spreadsheet with this stuff separated out with my points selected?
### P is constant at 10
    5792 + P = 5802
    
```{r}
mol_numbers <- mutate(M5_DE_all_CPX_KBH_94_23, P2O5/141.943,#Change file here
                  SiO2/53.083,
                  TiO2/79.865,
                  Al2O3/101.961,
                  Cr2O3/99.993,
                  MgO/40.304,
                  CaO/56.077,
                  MnO/70.937,
                  FeO/71.844,
                  NiO/74.692,
                  Na2O/61.979,
                  K2O/94.195)

atomic_prop_ca_ol <- mutate(mol_numbers, p = P2O5/141.943*5,
                        si = SiO2/53.083 * 2,
                        ti = TiO2/79.865 * 2,
                        al = Al2O3/101.961 * 3,
                        cr = Cr2O3/99.993 * 3,
                        mg = MgO/40.304 * 1,
                        ca = CaO/56.077 * 1,
                        mn = MnO/70.937 * 1,
                        fe = FeO/71.844 * 1,
                        ni = NiO/74.692 * 1,
                        na = Na2O/61.979 * 1,
                        k = K2O/94.195 * 1
                        )

```

# Calculation to find atomic proportion of Ca in CPX

```{r}
# Calculation to find atomic proportion of Ca in CPX

mol_numbers <- mutate(M5_DE_all_CPX_KBH_94_23, P2O5/141.943,#Change file here
                  SiO2/53.083,
                  TiO2/79.865,
                  Al2O3/101.961,
                  Cr2O3/99.993,
                  MgO/40.304,
                  CaO/56.077,
                  MnO/70.937,
                  FeO/71.844,
                  NiO/74.692,
                  Na2O/61.979,
                  K2O/94.195)

atomic_prop_ca_cpx <- mutate(mol_numbers, p = P2O5/141.943*5,
                        si = SiO2/53.083 * 2,
                        ti = TiO2/79.865 * 2,
                        al = Al2O3/101.961 * 3,
                        cr = Cr2O3/99.993 * 3,
                        mg = MgO/40.304 * 1,
                        ca = CaO/56.077 * 1,
                        mn = MnO/70.937 * 1,
                        fe = FeO/71.844 * 1,
                        ni = NiO/74.692 * 1,
                        na = Na2O/61.979 * 1,
                        k = K2O/94.195 * 1
                        )
```

# Temps calcs

```{r}
D_Ca <- mutate(# what is the dataset here?, 
                 D_Ca = atomic_prop_ca_ol/atomic_prop_ca_cpx,
                 ln_D_Ca = log(D_Ca),
                 x-T = (ln_D_Ca)*-1,
                 x42.5 = (x-T)*42.5,
                 sub_1.25 = (x42.5)-1.25,
                 42.5_div_5802 = 42.5 * 5802,
                 fin = (42.5_div_5802)/(sub_1.25),
                 con_cels = (fin) - 273.15
                 
                 
                )
```

